\documentclass[a4paper,11pt,twocolumn]{article}
\usepackage[english]{babel}
\usepackage[backend=biber]{biblatex}
\usepackage{csquotes}
\usepackage[top=1.2in, bottom=1in, left=1.4in, right=1.4in]{geometry}
\usepackage{hyperref}

\addbibresource{/home/deepak/deepak/Projects/Major/btech-project/references.bib}

\hypersetup{
	hidelinks,
	pdftitle={SCTP Sendbuffer Advertising},
	pdfauthor={Arpan Kapoor, Deepak Sirone J, K Prasad Krishnan},
	pdfsubject={Midterm Report},
}


\title{SCTP Sendbuffer Advertising\\
	{\normalsize CS4089 Project\\
		Midterm Report}}

\author{Arpan Kapoor, Deepak Sirone J, K Prasad Krishnan\\
	Guided By: Dr.~Vinod Pathari}

\begin{document}

\maketitle

\section{Introduction}
Stream Control Transport Protocol (SCTP) is a reliable transport protocol
designed to transport Public Switched Telephone Network (PSTN) signaling
messages over IP networks, but is capable of broader applications.

\section{Problem Statement}
To study the effects of advertising sendbuffer occupancy in SCTP. This
information allows networks to discern between application-limited,
network-limited and flow-control limited flows, creating new avenues of network
optimization.

\section{Literature Survey}
RFC 3286 \cite{rfc3286} provides a high level introduction to the capabilities
supported by SCTP, while RFC 4960 \cite{rfc4960} describes the complete
protocol. Agache and Raiciu \cite{tcp-sndbufadv} propose a scheme to advertise
sendbuffer occupancy in TCP.

\section{Work Done}
Wrote a file transfer utility that uses SCTP as the transport protocol to
measure the fluctuations in the sendbuffer size.

\section{Future Work}
To design a working prototype of sendbuffer advertising for SCTP in the Linux
kernel and test it in a simulated network. Security implications of the
prototype will also be studied.

\printbibliography

\end{document}
