% Copyright 2007 by Till Tantau
%
% This file may be distributed and/or modified
%
% 1. under the LaTeX Project Public License and/or
% 2. under the GNU Public License.
%
% See the file doc/licenses/LICENSE for more details.

\documentclass{beamer}
\setbeamertemplate{bibliography item}[text]
\title{SCTP Sendbuffer Advertising\\ {\normalsize CS4089 Project\\Midterm Evaluation}}
\author{Arpan Kapoor, Deepak Sirone J, K Prasad Krishnan\\Guided By: Dr. Vinod Pathari}
\date{September 18, 2015}
\begin{document}

\begin{frame}
  \titlepage
\end{frame}

\begin{frame}{Outline}
  \tableofcontents
\end{frame}
\section{Introduction}
\begin{frame}{Introduction}
\begin{itemize}
 \item Stream Control Transmission Protocol(SCTP):
\begin{itemize}
 \item is designed to transport Public Switched Telephone Network (PSTN) signaling messages
   over IP networks, but is capable of broader applications.
\end{itemize}
\begin{itemize}
 \item the next generation transport protocol which aims to remove several limitations of TCP
\end{itemize}
\end{itemize}
\begin{itemize}
 \item Sendbuffer Advertising:
\begin{itemize}
 \item each segment will carry the amount of backlogged data present in the sender's
   buffer   
\end{itemize}
\end{itemize}

\end{frame}

\section{Problem Statement}
\begin{frame}{Problem Statement}
\begin{itemize}
 \item To study the effects of advertising send-buffer occupancy in SCTP. 
This information allows networks to discern between application-limited, network-limited and flow-control limited flows, creating new avenues of network optimization.
\end{itemize}
\end{frame}

\section{Literature Survey }
\begin{frame}{Literature Survey }
\begin{itemize}
\item RFC 3286 \cite{much} provides a high level introduction to the capabilities supported by
SCTP . 
\item RFC 4960 \cite{sumit} describes the complete protocol
\item Agache and Raiciu \cite{aga} propose a scheme to advertise send-
buffer occupancy in TCP.
\end{itemize}
\end{frame}
\section{Work Done}
\begin{frame}{Work Done}
\begin{itemize}
 \item Completed a part of the planned literature survey
 \item Wrote a file transfer utility that uses SCTP as the transport protocol to measure the fluctuations in the sendbuffer size.
\end{itemize}
\end{frame}

\section{Future Work}
\begin{frame}{Future Work}
\begin{itemize}
\item To design a working prototype of sendbuffer advertising for SCTP in the Linux
kernel and test it in a simulated network.
 \item Security implications of the prototype will also be studied.
 
\end{itemize}
\end{frame}


\section{References}

\begin{frame}[allowframebreaks]
  \frametitle<presentation>{References}   

\begin{thebibliography}{100}
\bibitem{aga}
A. Agache and C. Raiciu.\textit{TCP Sendbuffer Advertising}.Internet-Draft draft-agache-tcpm-sndbufadv-00.txt.IETF Secretariat, July 20, 2015.
\bibitem{much}
L. Ong and J. Yoakum. \textit{An Introduction to the Stream Control Transmission Protocol (SCTP)}.RFC 3286. RFC Editor, May 2002,pp. 1–10.\newline url: http://www.rfc-editor.org/rfc/rfc3286.txt.
\bibitem{sumit}
R. Stewart. \textit{Stream Control Transmission Protocol}. RFC 4960. RFCEditor, Sept. 2007, pp. 1–152. \newline url: http : //www.rfc-editor.org/rfc/rfc4960.txt.
\end{thebibliography}{}
\end{frame}
\end{document}

