\documentclass[a4paper,11pt]{article}
\usepackage[english]{babel}
\usepackage[backend=biber]{biblatex}
\usepackage{bytefield}
\usepackage{csquotes}
\usepackage{geometry}
\usepackage[cleanup]{gnuplottex}
\usepackage{hyperref}

\addbibresource{../../references.bib}

\hypersetup{
  hidelinks,
  pdftitle={SCTP Sendbuffer Advertising},
  pdfauthor={Arpan Kapoor, Deepak Sirone J, K Prasad Krishnan},
  pdfsubject={End Semester Report},
}


\title{SCTP Sendbuffer Advertising\\
  {\normalsize CS4099 Project\\
    Midterm Report}}

\author{Arpan Kapoor (B120555CS)\\
  Deepak Sirone J (B120097CS)\\
  K Prasad Krishnan (B120128CS)\and
  Guided By:\\ Dr.~Vinod Pathari\\
  Mr.~V Anil Kumar, Principal Scientist, CSIR, Bengaluru}

\begin{document}

\maketitle

\section{Introduction}
Stream Control Transport Protocol (SCTP) is a reliable transport protocol
designed to transport Public Switched Telephone Network (PSTN) signaling
messages over IP networks, but is capable of broader applications.
Unlike TCP, SCTP offers sequenced delivery of user messages within multiple
unidirectional logical channels called streams.
Each SCTP endpoint is represented as a set of destination transport addresses,
one of which is the primary address. If the primary address becomes unreachable
SCTP chooses another destination transport address to route the messages 
thereafter. This provides network-level fault tolerance and is called
multi-homing.
It also employs a security cookie mechanism during association initialization
to provide resistance to flooding and masquerade attacks.

Advertising the amount of backlogged data present in the sender's buffer can
help network operators evaluate the end-to-end performance of a connection
in a better way than that with the existing passive measurements.
This information can also be used to infer whether a connection is limited
by the network or the application.

\section{Problem Statement}
To propose a scheme to advertise sendbuffer occupancy information in SCTP,
implement it in the Linux kernel and study the performance and security
implications of the same.

\section{Literature Survey}
RFC 3286 \cite{rfc3286} provides a high level introduction to the capabilities
supported by SCTP, while RFC 4960 \cite{rfc4960} describes the complete
protocol. Agache and Raiciu \cite{tcp-sndbufadv} propose a scheme to advertise
sendbuffer occupancy in TCP. \cite{budigerelinux} was used to study the state
machine employed in the Linux SCTP implementation. It was also used to 
understand the SCTP packet flow within the kernel.

\section{Work Done in the previous semester}
Initially, we wrote a file transfer utility that uses SCTP as the
transport protocol.
We modified a kernel module called \texttt{sctp\_probe} to measure and plot
the sendbuffer size at regular intervals during a file transfer performed
using our userspace program.

\begin{figure}[h]
  \centering
  \begin{gnuplot}[terminal=cairolatex]
    set xlabel 'Time (s)'
    set ylabel 'Sendbuffer Used (KB)\vspace{0.5cm}'
    set format y '%.0s'
    set key off
    set xrange [0:3700]
    plot '../../code/file_transfer/datafile' using ($1-1447078873):2 every 500 with lines
  \end{gnuplot}
  \caption{Sendbuffer variation during a 1 GB file transfer.}
\end{figure}

We explored the Linux kernel SCTP implementation to understand how the
data from userspace is transformed into a SCTP packet and sent to the network
layer.
The data structures related to the state information, specifically
the out queue were studied in detail. The parameter corresponding to the
sendbuffer information, which is to be advertised was identified.

\clearpage

\subsection{Design}
Each chunk is formatted with a Chunk Type field, a chunk-specific Flag field,
a Chunk Length field, and a Value field. Chunk Type, which takes a value
from 0 to 254, identifies the type of information contained in the Chunk
Value field. The Chunk Type values from 15 to 62, 64 to 126, 128 to 190 and
192 to 254 are not used presently in the SCTP implementation.
For advertising the sendbuffer occupancy,a new Chunk Type value is selected
from 128 to 190. RFC 4960 \cite{rfc4960} lays out the actions when
the processing endpoint does not recognize the Chunk Type (as is
the case here) depending on the highest order 2 bits. RFC 4960 \cite{rfc4960}
specifies that if the chunk is not recognised by the endpoint and the
highest order bits are 10, the chunk will be skipped without sending
an Unrecognized Chunk Type error chunk. This ensures that proposed
addition of a new Chunk Type would not affect hosts running the
unmodified SCTP linux implementation.

\begin{figure}[h]
  \centering
  \begin{bytefield}[bitwidth=1.1em]{32}
  \bitheader{0-31}\\
  \bitbox{8}{Chunk Type} & \bitbox{8}{Chunk Flags} & \bitbox{16}{Chunk Length}\\
  \bitbox{32}{Sendbuffer size}
  \end{bytefield}
  \caption{Proposed Chunk for sendbuffer advertisement}
\end{figure}

The overhead of 8 bytes which can come up in the proposed solution
is considerable as it is just 0.53\% of a 1500 byte packet.


\section{Work Done in the current semester}
A working prototype of sendbuffer advertisement was implemented in the Linux
kernel. The interval for sending the sendbuffer advertisement chunk can be
modified at runtime.


\section{Future Work and Conclusions}
To test the prototype of sendbuffer advertising for SCTP in the Linux kernel
in a network. Security implications of the prototype will also be studied.

There are several scheduling algorithms which prioritizes packets based on some
criteria. One of these priority based scheduling algorithms can be modified to
consider the sendbuffer information and to improve QoS for high volume flows.

\clearpage
\printbibliography

\end{document}
